My title

### 2024-03-11 paper/paper.qmd
organize the structure

@@

```
```{r}
# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.

pp_check(political_preferences1) +
  theme(legend.position = "bottom")
```
```{r}

# marginal effect -- ?

slopes(political_preferences1) |>
  summary() |>
  select(-term) |>
  kable(
    col.names = c("Compare department", "Estimate", "2.5%", "97.5%"),
    digits = 2, booktabs = TRUE, linesep = ""
  )
```

>>>>

-------------------------------needs some explanation
```{r}
# We could use posterior predictive checks, introduced in Section 12.4, to show that the logistic regression approach is a good choice for this circumstance.

pp_check(political_preferences1) +
  theme(legend.position = "bottom")
```

```{r stateplot, echo=F, message=F, warning=F, fig.cap="Proportion of each State Voting for Biden"}
# get state by state proportions for our polling data
polling_props <- polling %>% 
  group_by(stateicp, vote_biden) %>% 
  summarise(n = n()) %>% 
  mutate(prop = n/sum(n))

# combine the polling data proportions with the post-stratification data
poll_post_biden <- inner_join(polling_props, voting_biden, by = "stateicp")
poll_post_biden <- poll_post_biden %>% 
  filter(vote_biden == 1)

# plot for predictions

poll_post_biden %>% 
  ggplot(aes(x = stateicp, y = biden_predict)) +
  geom_point(aes(color = "black")) +
  geom_line(aes(group = 1)) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 70, size = 6, hjust = 1)) +
  geom_ribbon(aes(group = 1, ymin=biden_predict_lower, ymax=biden_predict_upper), 
              alpha = 0.2, fill = "red") +
  geom_line(data = poll_post_biden, aes(x=stateicp, y=prop, group = 2), 
            linetype = "twodash") +
  geom_point(data = poll_post_biden, aes(x=stateicp, y=prop, colour = "red")) +
  geom_hline(aes(yintercept = 0.5), alpha = 0.5) +
  scale_color_discrete(name = "Data", labels = c("Population", "Sample")) +
  labs(title = "Proportion of People voting for Joe Biden by State",
       x = "State", y = "Percentage Voting Biden")
```

@@
